\documentclass{s8g_base}
\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{%
  Highly motivated modder and programmer with a passion for creating compelling user experiences and innovative game engines. Seeking an entry-level position in the game industry to leverage expertise in UI development, cross-platform builds, and customer support. Proven ability to impact thousands of users daily as a contributor to the OpenMW modding community. Eager to contribute to a professional team and deliver exceptional results.
}
%
%
%Education
\section{Education} 
    \datedexperience{Holberton Tulsa}{2022-2023}
    \explanation{AR/VR Engineering \& Game Design}
    \explanationdetail{
      \coloredbullet\ Immersive 20-month program covering Linux, C programming fundamentals, AR/VR development, and game design principles. \\
      \coloredbullet\ Collaborated on diverse projects employing agile methodologies and version control, gaining experience with frameworks such as Flask and the Unity game engine.
    }
     %
     %
     %
    \datedexperience{Tulsa Tech Riverside}{2015-2016}
    \explanation{Computer Repair \& Network Technology}
    \explanationdetail{
      \coloredbullet\ Completed an intensive lab-focused A+ certification course, providing a solid foundation in computer hardware and system administration principles. \\
      \coloredbullet\ Gained hands-on experience building, diagnosing, and repairing Windows, Mac, and Linux systems, developing valuable troubleshooting and problem-solving skills applicable to game development environments.
    }
%
%
%
\section{Major Projects}
% Morrobroom
\explanation{\href{https://github.com/magicaldave/Morrobroom}{Morrobroom} - Use quake modding tools to develop OpenMW content and 3D assets. \href{https://openmw.org/2024/from-bsp-to-esp-how-s3ctor-abused-quake-editors-to-redefine-the-morrowind-modding-experience/}{More on OpenMW's Blog}}
% St4sh
\explanation{\href{https://modding-openmw.gitlab.io/s3ctors-s3cret-st4sh/}{S3ctor's S3cret St4sh} - Umbrella site for my OpenMW Mods. Built with Soupault, hosted on GitLab}
% MMW
\explanation{\href{https://morrowind-modding.github.io}{The Morrowind Modding Wiki} - Curated Morrowind/OpenMW modding guides. Built with TypeScript in Quartz}
% OpenMW
\explanation{\href{https://gitlab.com/OpenMW/openmw}{OpenMW} - Developing OpenMW's content editor \& Lua API for the creation of new games}
% Experience
\section{Experience}
%
%
\datedexperience{Conduent Business Services}{Mar 2017-Jan 2019}
\explanation{Technical Support Advisor Tier 2}
\explanationdetail{
  \coloredbullet\ Provided comprehensive technical support for diverse hardware and software, including debugging, troubleshooting, and problem resolution across multiple platforms. \\
  \coloredbullet\ Managed complex technical issues from initial report to resolution, demonstrating ownership and attention to detail. \\
  \coloredbullet\ Mentored new team members, fostering a collaborative environment and enhancing team knowledge.
}
%
%
\datedexperience{United States Cellular Corporation}{2019}
\explanation{Frontline Customer Service Representative}
\explanationdetail{
  \coloredbullet\ Provided initial support for billing and technical issues, effectively triaging customer inquiries and escalating complex problems as needed. \\
  \coloredbullet\ Assisted customers with new device setup, recommended relevant third-party solutions, and presented additional service options, demonstrating strong communication and sales skills.
}
%
%
%
% Skills
\section{Skills}
%
%
\newcommand{\skillone}{\createskill{Programming Languages}{
    \textbf{\emph{Experienced:}} \ \
    Rust
    \cpshalf
    C++
    \cpshalf
    Lua
    \cpshalf
    Bash
    \ \ \textbf{\emph{Familiar:}} \ \
    Javascript
    \cpshalf
    Python
    \cpshalf
    Emacs Lisp
}}
    %
\newcommand{\skilltwo}{\createskill{Software Development}{
    Git
    \cpshalf
    CLI
    \cpshalf
    Linux
    \cpshalf
    CMake
    \cpshalf
    GitHub Actions
    \cpshalf
    GitLab Pipelines
    \cpshalf
    DevOps
    \cpshalf
    Emacs
}}
%
%
\newcommand{\skillthree}{\createskill{Frameworks \ \& \ Libraries}{
    myGUI
    \cpshalf
    LuaJIT
    \cpshalf
    ImageMagick
    \cpshalf
    Qt
    \cpshalf
    Tauri
    \cpshalf
    Docker
    \cpshalf
    Flask
    \cpshalf
    React
    \cpshalf
    Material UI
}}
%
%
\newcommand{\skillfour}{\createskill{Development Focus}{
    User Interface/Experience
    \cpshalf
    Automation
    \cpshalf
    Cross-platform Applications
    \cpshalf
    Application Distribution
}}
%
%% \newcommand{\skillfive}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  English \ \ \textbf{\emph{Beginner:}} \ \  French }}
%
\createskills{\skillone, \skilltwo, \skillthree, \skillfour}
%
%
%
%
%
% Experience
\section{Extra}
\explanation{
  \coloredbullet\
  Passionate about level design and game mechanics
}
%
%
\explanation{
  \coloredbullet\
  Committed to open source and community knowledge sharing
}
%
%
%
%
%Footnote
\createfootnote
\end{document}
